PS753 Glossary

### 2022-02-28 _academics/ps753-glossary/ps753-glossary.Rmd
Add terms

eigenvector centrality
: "takes into account the centrality of other nodes to which a node is connected. That is, being connected to other central nodes increases centrality." Takes into account the centrality of the nodes a node is connected to, considering the importance of the connected nodes and not just their quantity or path length.
$$\lambda \text{c} = \text{Wc}$$

Bonacich Power
: "A closely related concept, but includes a weighting factor that emphasizes global vs. local structure (and negative connections)"
$$\text{c}(\alpha, \beta) = \alpha(\text{I} - \beta\text{W})^{-1}\text{W1}$$

@@

betweenness centrality
: (forthcoming)

>>>>

eigenvector centrality
: "takes into account the centrality of other nodes to which a node is connected. That is, being connected to other central nodes increases centrality." Takes into account the centrality of the nodes a node is connected to, considering the importance of the connected nodes and not just their quantity or path length. A node with high eigenvector centrality is connected to significant numbers of other highly central nodes.
$$\lambda \text{c} = \text{Wc}$$

Bonacich Power
: "A closely related concept, but includes a weighting factor that emphasizes global vs. local structure (and negative connections)" In contrast to eigenvector centrality, penalizes nodes connected to other well-connected nodes, under the theory that being connected to strong or powerful nodes means a node has less influence and power than it would if it were connected to fewer or weaker nodes.
$$\text{c}(\alpha, \beta) = \alpha(\text{I} - \beta\text{W})^{-1}\text{W1}$$

@@

betweenness centrality
: a count of the number of shortest paths between nodes that pass through another node
